The Role of Variability in Learning Generalization: A Computational Modeling Approach

### 2024-06-02 Presentation/slides.qmd
final changes pre-presentation

::: notes
- Variety of theoretical explanations have been proposed for the commonly observed effects
- In visuomotor learning and most relevant for my work, Schema theory in paticular has been extremely influential, and seems to have inspired hundreds of studies
:::

@@

::: fragment
:::: columns
::: {.column}

![](assets/agg_issues.png)
:::
::: {.column}

::::
:::
::: footnote
e.g. [@mccrackenTestSchemaTheory1977; @chuaPracticeVariabilityPromotes2019; @delreyEffectsContextualInterference1982]
:::

::: notes
- Schema theory assumes that learners encode abstractions, or parameters, that enable generalization, and that variation is parituiclarly helpful
:::

>>>>

::: notes
- Variety of theoretical explanations have been proposed for the commonly observed effects
- In visuomotor learning and most relevant for my work, Schema theory in paticular has been extremely influential, and seems to have inspired hundreds of studies
- Unlike the models I'll be presenting today, at least to my knowledge none of these have ever been formally specified and actually fit to human data
:::

@@

::: notes
- Schema theory assumes that learners encode abstractions, or parameters, that enable generalization, and that variation is parituiclarly helpful
- failures to consider nonlinear effects of learning 
- failure to consider that, through lieu of being exposed to broader coverage of the task space, varied training manipulations can often 
:::
